---
title: "Pop Quiz"
output: pdf_document
---

```{r setup, echo=FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE)
```



# Please complete the following  

Assume that you have the following packages loaded:

```{r message=FALSE}
library('kableExtra')
library('tidyverse')
library('caret')

# Output function for printing to pdf
tbl_out = function(df, rows = 10){
  head(df, rows) %>%
    kable() %>%
    kable_styling()
  }
```


Given the `iris` data set (first 10 rows shown below):  
```{r}
dat = iris %>% as_tibble()
tbl_out(dat)
```

\newpage

In words, describe what you would expect this to return:
```{r echo=TRUE, message=FALSE, eval=FALSE}
dat %>% 
  sample_n(nrow(dat)) %>%
  tbl_out()
```
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  

Assuming your data is "clean" and your EDA has been accomplished. What steps would you take to get your data prepared for a classification algorithm?  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  

\newpage 
  
Show the rough code you would use to get your data ready and then train a model using `caret` and show how you would analyze and look at the results.   -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  
  -  